Analysis of Retrospective COVID-19 data

### 2020-10-19 manuscript/analysis_brms.Rmd
update brms analysis

```{r}
# all patients for which we have data for at least 7 days
# data$surv_data_7 <- data$surv_data %>%
#   group_by(patient_id) %>%
#   filter(!(max(day) < 7 & outcome3 == "Hospitalized")) %>%
#   ungroup()
#  
# 
# # all patients for which we have data for at least 7 days
# data$surv_data_28 <- data$surv_data_last_day %>%
#   filter(!(day < 28 & outcome3 == "Hospitalized"))

# Note: the code above can IMHO introduce biases if there is some systematic skew that makes patients not have a final outcome after day 7 if they are more/less likely to have good outcomes. Instead, I _think_ we need to have "state at day 7", i.e. patients that died/were discharged after day 7 are still treated as "Hospitalized" for the analysis. Additionally, other studies (e.g. RECOVERY) work this way. This is how I would code this:

surv_data_at_day <- function(patient_data, day) {
  res <- patient_data %>%
    filter(!(last_record < day & outcome3 == "Hospitalized"))

  #Non tidy to avoid hassle with factor levels  
  res$outcome3[res$last_record > day] <- "Hospitalized"
  res
}

@@

- first and last day invasive: Martin will check
- days_from_symptom_onset. Days from symptom onset until hospitalization. 
Uncertain marker but contains some information. 
Required for anti viral (< 7 days) hypothesis.
- first_day_*: time from day 0 (arrived at hospital) to getting antivirals
- some sites only support patients with mild disease and some only with
strong disease symptoms

@@

```{r, results="hide"}
form_survival_base <- bf(
  survival ~ sex + age_norm + 
    smoking + BMI + ever_hcq + ever_az +
    (1 | hospital_id),
  family = bernoulli("logit")
)

@@

```{r}
draws <- tidy_draws(fit_survival_base)
hypothesis_res_list[["hcq_az_survival_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_base_7)
hypothesis_res_list[["hcq_az_survival_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_base_28)
hypothesis_res_list[["hcq_az_survival_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

### TODOs

- model varying slopes?
- model interactions?
- use horseshoe prior
- use projpred
- add ever_keltara as soon as there is a lest one patient who took it.

@@

```{r, results="hide"}
form_survival_time <- bf(
  day | cens(censored) ~ sex + age_norm + 
    smoking + BMI + ever_hcq + ever_az + 
    (1 | hospital_id),
  family = brmsfamily("cox", "log")
)

@@

```{r}
draws <- tidy_draws(fit_survival_time)
hypothesis_res_list[["hcq_az_survival_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

### TODOs:

- How does that relate to days of hospitalization? (Answer: could be analysed;
could be an interesting end point when people are discharged)

@@

```{r, results="hide"}
form_discharged_base <- bf(
  discharged ~ sex + age_norm + 
    smoking + BMI + ever_hcq + ever_az +
    (1 | hospital_id),
  family = bernoulli("logit")
)

@@

```{r}
draws <- tidy_draws(fit_discharged_base)
hypothesis_res_list[["hcq_az_discharged_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base_7)
hypothesis_res_list[["hcq_az_discharged_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base_28)
hypothesis_res_list[["hcq_az_discharged_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

### TODOs

- model varying slopes?
- model interactions?
- use horseshoe prior
- use projpred
- add ever_keltara as soon as there is a lest one patient who took it.

@@

```{r, results="hide"}
form_discharged_time <- bf(
  day | cens(censored_discharged) ~ sex + age_norm + 
    smoking + BMI + ever_hcq + ever_az + 
    (1 | hospital_id),
  family = brmsfamily("cox", "log")
)

@@

```{r}
draws <- tidy_draws(fit_discharged_time)
hypothesis_res_list[["hcq_az_discharged_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r, results="hide"}
form_outcome_base <- bf(
  outcome3 ~ sex + age_norm + 
    smoking + BMI + ever_hcq + ever_az +
    (1 | hospital_id),
  family = categorical("logit")
)

@@

```{r}
draws <- tidy_draws(fit_outcome_base)
hypothesis_res_list[["hcq_az_outcome_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_outcome_base_7)
hypothesis_res_list[["hcq_az_outcome_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_outcome_base_28)
hypothesis_res_list[["hcq_az_outcome_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, sex, age_norm, smoking, BMI"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, sex, age_norm, smoking, BMI"
  )
)
```

@@

```{r, results="hide"}
form_worst_breathing_base <- bf(
  worst_breathing ~ sex + age_norm + 
    smoking + BMI + ever_hcq + ever_az +
    (1 | hospital_id),
  family = sratio("logit")
)

@@

```{r, results="hide"}
form_worst_breathing_cs <- bf(
  worst_breathing ~ cs(sex + age_norm + 
    smoking + BMI + ever_hcq + ever_az) +
    (1 | hospital_id),
  family = sratio("logit")
)

prior_worst_breathing_cs <- 
  prior(normal(0, 5), class = "b") +
  prior(normal(0, 5), class = "sd")

fit_worst_breathing_cs <- brm(
  formula = form_worst_breathing_cs,
  data = data$patient_data,
  prior = prior_worst_breathing_cs,
  inits = 0,
  file = "models/fit_worst_breathing_cs"
)
fit_worst_breathing_cs <- add_criterion(fit_worst_breathing_cs, "loo")
```

```{r}
summary(fit_worst_breathing_cs)
# ce <- conditional_effects(fit_worst_breathing_cs, categorical = TRUE)
# plot(ce, ask = FALSE)
```

@@

```{r}
loo(fit_worst_breathing_base, fit_worst_breathing_cs)
```

### TODOs

- How to handle missing values in `worst_breathing`?
- decide which predictors to include 
- model interactions?
- model varying slopes?
- use horseshoe or similar sparsity priors?

>>>>

```{r}
# we need to have "state at day 7", i.e. patients that died/were discharged 
# after day 7 are still treated as "Hospitalized" for the analysis. Other 
# studies (e.g. RECOVERY) work this way. Code provided by Martin.
surv_data_at_day <- function(patient_data, day) {
  res <- patient_data %>%
    filter(!(last_record < day & outcome3 == "Hospitalized"))

  # Non tidy to avoid hassle with factor levels  
  res$outcome3[res$last_record > day] <- "Hospitalized"
  res
}

@@

- days_from_symptom_onset. Days from symptom onset until hospitalization. 
Uncertain marker but contains some information. 
Required for anti viral (< 7 days) hypothesis.
- first_day_*: time from day 0 (arrived at hospital) to getting antivirals
- some sites only support patients with mild disease and some only with
strong disease symptoms

@@

```{r, results="hide"}
form_survival_base <- bf(
  survival ~ sex + age_norm + 
    smoking + mo(obesity) + ever_hcq + ever_az + ever_favipiravir +
    (1 | hospital_id),
  family = bernoulli("logit")
)

@@

```{r}
draws <- tidy_draws(fit_survival_base)
hypothesis_res_list[["hcq_az_survival_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_base_7)
hypothesis_res_list[["hcq_az_survival_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_7",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_survival_base_28)
hypothesis_res_list[["hcq_az_survival_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_28",
    estimand = "logit(survival)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r, results="hide"}
form_survival_time <- bf(
  day | cens(censored) ~ sex + age_norm + 
    smoking + mo(obesity) + ever_hcq + ever_az + ever_favipiravir +
    (1 | hospital_id),
  family = brmsfamily("cox", "log")
)

@@

```{r}
draws <- tidy_draws(fit_survival_time)
hypothesis_res_list[["hcq_az_survival_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r, results="hide"}
form_discharged_base <- bf(
  discharged ~ sex + age_norm + 
    smoking + mo(obesity) + ever_hcq + ever_az + ever_favipiravir +
    (1 | hospital_id),
  family = bernoulli("logit")
)

@@

```{r}
draws <- tidy_draws(fit_discharged_base)
hypothesis_res_list[["hcq_az_discharged_base"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base_7)
hypothesis_res_list[["hcq_az_discharged_base_7"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_discharged_base_28)
hypothesis_res_list[["hcq_az_discharged_base_28"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiravirTRUE,
    model = "brms_binary_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r, results="hide"}
form_discharged_time <- bf(
  day | cens(censored_discharged) ~ sex + age_norm + 
    smoking + mo(obesity) + ever_hcq + ever_az + ever_favipiravir +
    (1 | hospital_id),
  family = brmsfamily("cox", "log")
)

@@

```{r}
draws <- tidy_draws(fit_discharged_time)
hypothesis_res_list[["hcq_az_discharged_time"]] <- rbind(
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_hcqTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_azTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_ever_favipiraviTRUE,
    model = "brms_cox",
    estimand = "log(HR)",
    hypothesis = hypotheses$favipiravi_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r, results="hide"}
form_outcome_base <- bf(
  outcome3 ~ sex + age_norm + 
    smoking + mo(obesity) + ever_hcq + ever_az + ever_favipiravir +
    (1 | hospital_id),
  family = categorical("logit")
)

@@

```{r}
draws <- tidy_draws(fit_outcome_base)
hypothesis_res_list[["hcq_az_outcome_base"]] <- rbind(
  # Death 
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_outcome_base_7)
hypothesis_res_list[["hcq_az_outcome_base_7"]] <- rbind(
  # Death 
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical_7",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical_7",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r}
draws <- tidy_draws(fit_outcome_base_28)
hypothesis_res_list[["hcq_az_outcome_base_28"]] <- rbind(
  # Death
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_hcqTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$hcq_reduces_death,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_azTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$az_reduces_death,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDeath_ever_favipiravirTRUE,
    model = "brms_categorical_28",
    estimand = "logit(death)",
    hypothesis = hypotheses$favipiravir_reduces_death,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  ),
  # Discharged
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_hcqTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$hcq_increases_discharged,
    adjusted = "az, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_azTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$az_increases_discharged,
    adjusted = "hcq, favipiravir, sex, age_norm, smoking, obesity"
  ),
  bayesian_hypothesis_res_from_draws(
    draws = draws$b_muDischarged_ever_favipiravirTRUE,
    model = "brms_categorical_28",
    estimand = "logit(discharged)",
    hypothesis = hypotheses$favipiravir_increases_discharged,
    adjusted = "hcq, az, sex, age_norm, smoking, obesity"
  )
)
```

@@

```{r, results="hide"}
form_worst_breathing_base <- bf(
  worst_breathing ~ sex + age_norm + 
    smoking + mo(obesity) + ever_hcq + ever_az + ever_favipiravir +
    (1 | hospital_id),
  family = sratio("logit")
)

@@

```{r, results="hide"}
# form_worst_breathing_cs <- bf(
#   worst_breathing ~ cs(sex + age_norm + 
#     smoking + mo(obesity) + ever_hcq + ever_az + ever_favipiravir) +
#     (1 | hospital_id),
#   family = sratio("logit")
# )
# 
# prior_worst_breathing_cs <- 
#   prior(normal(0, 5), class = "b") +
#   prior(normal(0, 5), class = "sd")
# 
# fit_worst_breathing_cs <- brm(
#   formula = form_worst_breathing_cs,
#   data = data$patient_data,
#   prior = prior_worst_breathing_cs,
#   inits = 0,
#   file = paste0(cache_dir, "/fit_worst_breathing_cs")
# )
# fit_worst_breathing_cs <- add_criterion(fit_worst_breathing_cs, "loo")
```

```{r}
# summary(fit_worst_breathing_cs)
# ce <- conditional_effects(fit_worst_breathing_cs, categorical = TRUE)
# plot(ce, ask = FALSE)
```

@@

```{r}
# loo(fit_worst_breathing_base, fit_worst_breathing_cs)
```

## Store Hypotheses
